---
title: "e2e_preprocessing_cleaning_anm"
author: "Amanda Moeller"
date: "4/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages:
```{r}
library(tm)
#library(quanteda)
#library(tokenizers)
library(tidyr)
```

Bring in the data:
```{r}
devset <-read.csv("/Users/amandamoeller/Desktop/CSE 597 NLP/final project/e2e-dataset/devset.csv")
testset_w_refs <- read.csv("/Users/amandamoeller/Desktop/CSE 597 NLP/final project/e2e-dataset/testset_w_refs.csv")


# combine devset and testset_w_refs, clean, split 70/30

# create combined df:
dev_test_combo <- rbind(devset, testset_w_refs)

# split mr column on comma
df <- data.frame(dev_test_combo)
df <- separate(data = df, col = mr, into = c("1", "2", "3", "4", "5", "6", "7"), sep = "],")

# separate by rows
as_tibble(df)

df$`1` <- as.character(df$`1`)


data_list <- split(df, f = df$`1`)                    # Split data by restaurant name
data_list                                             # Print list of datasets


# 120, 220, 18, 228, 233, 173, 292 
# 243, 468, 222, 240, 6, 78, 32, 105, 
# 212, 858, 679, 263, 662, 709, 88, 912
# 581, 262, 991, 96, 342, 32

# sorted:
# 991, 912, 858, 709, 679, 662, 581, 468, 342, 292, 263, 262, 243, 240, 233, 228, 222, 220, 212, 173, 120, 105, 96, 88, 78, 32, 32, 18, 6

list2env(data_list,envir=.GlobalEnv) # saves dataframes to environment

wrestlers_991 <- `name[The Wrestlers`

wrestlers_991 
wrestlers_991$famfriend <- wrestlers_991$`3` # column 3 is familyFrindly[yes] and [no]
wrestlers_991$famfriend <- as.factor(wrestlers_991$famfriend)
wrestlers_991$famfriend # 352:991 are out of order (shows food type, not fam friend)

loch_6 <- `name[Loch Fyne`
loch_6 # eatType: 3 say coffee shop, 3 say pub
loch_6$eatType <- as.factor(loch_6$`2`)
loch_6$eatType




# RELIABILITY STUFF BELOW:
# ### just a note: number of raters here refers to the number of reviews of a single restaurant


# LOCH INTERRATER RELIABILITY:
loch_6$eatType <- factor(loch_6$`2`, levels = as.character(unique(loch_6$`2`))) # Convert character vector to factor

as.numeric(loch_6$eatType) # Convert to numeric   # 1 = coffee shop, 2 = pub

loch_6_t <- as.data.frame(t(loch_6)) # convert columns to rows
loch_6_t

library(irr)
a <- kappam.fleiss(loch_6_t[, 1:6]) # fleiss kappa = 0.47


# now do the above ^ for all restaurants:


# ALIMENTUM INTERRATER RELIABILITY: ############################################
alimen_8 <- `name[Alimentum`
alimen_8 

alimen_8 <- lapply(alimen_8, factor)  # convert all to factors
sapply(alimen_8, class)
alimen_8 <- as.data.frame(alimen_8)

library(dplyr) # remove refs 
select(alimen_8, -c(8))


alimen_8_t <- as.data.frame(t(alimen_8)) # transpose
alimen_8_t

# kappa
b <- kappam.fleiss(alimen_8_t[, 1:8]) # kappa = 0.57

# AROMI INTERRATER RELIABILITY: ############################################
aromi_220 <- `name[Aromi`
aromi_220 

aromi_220 <- lapply(aromi_220, factor)  # convert all to factors
sapply(aromi_220, class)
aromi_220 <- as.data.frame(aromi_220)

library(dplyr) # remove refs 
select(aromi_220, -c(8))

aromi_220_t <- as.data.frame(t(aromi_220)) # transpose
aromi_220_t

# kappa
c <- kappam.fleiss(aromi_220_t[, 1:220]) # kappa = 0.55

# BIBIMBAP INTERRATER RELIABILITY: ############################################
bibi_18 <- `name[Bibimbap House`
bibi_18 

bibi_18 <- lapply(bibi_18, factor)  # convert all to factors
sapply(bibi_18 , class)
bibi_18 <- as.data.frame(bibi_18)

library(dplyr) # remove refs 
select(bibi_18, -c(8))


bibi_18_t <- as.data.frame(t(bibi_18)) # transpose
bibi_18_t

# kappa
d <- kappam.fleiss(bibi_18_t[, 1:18]) # kappa = 0.56

# BLUE SPICE INTERRATER RELIABILITY: ############################################
blue_228 <- `name[Blue Spice`
blue_228 

blue_228 <- lapply(blue_228, factor)  # convert all to factors
sapply(blue_228 , class)
blue_228 <- as.data.frame(blue_228)


blue_228_t <- as.data.frame(t(blue_228)) # transpose
blue_228_t

library(dplyr) # remove refs 
select(blue_228, -c(8))

# kappa
e <- kappam.fleiss(blue_228_t[, 1:228]) # kappa = 0.39


# BROWNS CAMBRIDGE INTERRATER RELIABILITY: ############################################
brown_233 <- `name[Browns Cambridge`
brown_233 

brown_233 <- lapply(brown_233, factor)  # convert all to factors
sapply(brown_233 , class)
brown_233 <- as.data.frame(brown_233)


brown_233_t <- as.data.frame(t(brown_233)) # transpose
brown_233_t

library(dplyr) # remove refs 
select(brown_233, -c(8))

# kappa
f <- kappam.fleiss(brown_233_t[, 1:233]) # kappa = 0.57

# CLOWNS INTERRATER RELIABILITY: ############################################
clowns_173<- `name[Clowns`
clowns_173

clowns_173 <- lapply(clowns_173, factor)  # convert all to factors
sapply(clowns_173, class)
clowns_173 <- as.data.frame(clowns_173)


clowns_173_t <- as.data.frame(t(clowns_173)) # transpose
clowns_173_t

library(dplyr) # remove refs 
select(clowns_173, -c(8))

# kappa
g <- kappam.fleiss(clowns_173_t[, 1:173]) # kappa = 0.47

# COCUM INTERRATER RELIABILITY: ############################################
cocum_292 <- `name[Cocum`
cocum_292

cocum_292 <- lapply(cocum_292, factor)  # convert all to factors
sapply(cocum_292, class)
cocum_292 <- as.data.frame(cocum_292)


cocum_292_t <- as.data.frame(t(cocum_292)) # transpose
cocum_292_t

library(dplyr) # remove refs 
cocum_292 <- select(cocum_292, -c(8))

# kappa
h <- kappam.fleiss(cocum_292_t[, 1:292]) # kappa = 0.49

# COTTO INTERRATER RELIABILITY: ############################################
cotto_243 <- `name[Cotto`
cotto_243

cotto_243 <- lapply(cotto_243, factor)  # convert all to factors
sapply(cotto_243, class)
cotto_243 <- as.data.frame(cotto_243)


cotto_243_t <- as.data.frame(t(cotto_243)) # transpose
cotto_243_t

library(dplyr) # remove refs 
cotto_243 <- select(cotto_243, -c(8))

# kappa
i <- kappam.fleiss(cotto_243_t[, 1:243]) # kappa = 0.55


# FITZBILLIES INTERRATER RELIABILITY: ############################################
fitz <- `name[Fitzbillies`
fitz

fitz <- lapply(fitz, factor)  # convert all to factors
sapply(fitz, class)
fitz <- as.data.frame(fitz)

library(dplyr) # remove refs 
fitz <- select(fitz, -c(8))

fitz_t <- as.data.frame(t(fitz)) # transpose
fitz_t

# kappa
j <- kappam.fleiss(fitz_t[, 1:468]) # kappa = 0.51

# GIRAFFE INTERRATER RELIABILITY: ############################################
giraffe <- `name[Giraffe`

giraffe <- lapply(giraffe, factor)  # convert all to factors
giraffe <- as.data.frame(giraffe)

giraffe <- select(giraffe, -c(8)) # remove refs 

giraffe_t <- as.data.frame(t(giraffe)) # transpose

# kappa
k <- kappam.fleiss(giraffe_t[, 1:222]) # kappa = 0.55

# GREEN MAN INTERRATER RELIABILITY: ############################################
green <- `name[Green Man`

green <- lapply(green, factor)  # convert all to factors
green <- as.data.frame(green)

green <- select(green, -c(8)) # remove refs 

green <- as.data.frame(t(green)) # transpose

# kappa
l <- kappam.fleiss(green[, 1:240]) # kappa = 0.56

# LOCH FYNE INTERRATER RELIABILITY: ############################################
#loch <- `name[Loch Fyne`

#loch <- lapply(loch, factor)  # convert all to factors
#loch <- as.data.frame(loch)

#loch <- select(loch, -c(8)) # remove refs 

#loch <- as.data.frame(t(loch)) # transpose

# kappa
#m <- kappam.fleiss(loch[, 1:6]) # kappa = 0.72

# Midsummer House INTERRATER RELIABILITY: ############################################
mids <- `name[Midsummer House`

mids <- lapply(mids, factor)  # convert all to factors
mids <- as.data.frame(mids)

mids <- select(mids, -c(8)) # remove refs 

mids <- as.data.frame(t(mids)) # transpose

# kappa
m <- kappam.fleiss(mids[, 1:78]) # kappa = 0.63

# Strada INTERRATER RELIABILITY: ############################################
strada <- `name[Strada`

strada <- lapply(strada, factor)  # convert all to factors
strada <- as.data.frame(strada)

strada <- select(strada, -c(8)) # remove refs 

strada <- as.data.frame(t(strada)) # transpose

# kappa
n <- kappam.fleiss(strada[, 1:32]) # kappa = 0.50

# Taste of Cambridge INTERRATER RELIABILITY: ############################################
taste <- `name[Taste of Cambridge`

taste <- lapply(taste, factor)  # convert all to factors
taste<- as.data.frame(taste)

taste <- select(taste, -c(8)) # remove refs 

taste <- as.data.frame(t(taste)) # transpose

# kappa
o <- kappam.fleiss(taste[, 1:105]) # kappa = 0.76

# The Cambridge Blue INTERRATER RELIABILITY: ############################################
camblue <- `name[The Cambridge Blue`

camblue <- lapply(camblue, factor)  # convert all to factors
camblue<- as.data.frame(camblue)

camblue <- select(camblue, -c(8)) # remove refs 

camblue <- as.data.frame(t(camblue)) # transpose

# kappa
p <- kappam.fleiss(camblue[, 1:212]) # kappa = 0.73

# The Cricketers INTERRATER RELIABILITY: ############################################
cricket <- `name[The Cricketers`

cricket <- lapply(cricket, factor)  # convert all to factors
cricket<- as.data.frame(cricket)

cricket <- select(cricket, -c(8)) # remove refs 

cricket <- as.data.frame(t(cricket)) # transpose

# kappa
q <- kappam.fleiss(cricket[, 1:858]) # kappa = 0.34

# The Eagle INTERRATER RELIABILITY: ############################################
eagle <- `name[The Eagle`

eagle <- lapply(eagle, factor)  # convert all to factors
eagle <- as.data.frame(eagle)

eagle <- select(eagle, -c(8)) # remove refs 

eagle <- as.data.frame(t(eagle)) # transpose

# kappa
r <- kappam.fleiss(eagle[, 1:679]) # kappa = 0.37

# The Golden Palace INTERRATER RELIABILITY: ############################################
gold <- `name[The Golden Palace`

gold <- lapply(gold, factor)  # convert all to factors
gold <- as.data.frame(gold)

gold <- select(gold, -c(8)) # remove refs 

gold <- as.data.frame(t(gold)) # transpose

# kappa
s <- kappam.fleiss(gold[, 1:263]) # kappa = 0.52


# The Mill INTERRATER RELIABILITY: ############################################
mill <- `name[The Mill`

mill <- lapply(mill, factor)  # convert all to factors
mill <- as.data.frame(mill)

mill <- select(mill, -c(8)) # remove refs 

mill <- as.data.frame(t(mill)) # transpose

# kappa
t <- kappam.fleiss(mill[, 1:662]) # kappa = 0.34

# The Phoenix INTERRATER RELIABILITY: ############################################
phx <- `name[The Phoenix`

phx <- lapply(phx, factor)  # convert all to factors
phx <- as.data.frame(phx)

phx <- select(phx, -c(8)) # remove refs 

phx <- as.data.frame(t(phx)) # transpose

# kappa
u <- kappam.fleiss(phx[, 1:709]) # kappa = 0.49

# The Plough INTERRATER RELIABILITY: ############################################
plough <- `name[The Plough`

plough <- lapply(plough, factor)  # convert all to factors
plough <- as.data.frame(plough)

plough <- select(plough, -c(8)) # remove refs 

plough <- as.data.frame(t(plough)) # transpose

# kappa
v <- kappam.fleiss(plough[, 1:88]) # kappa = 0.66

# The Punter INTERRATER RELIABILITY: ############################################
punt <- `name[The Punter`

punt <- lapply(punt, factor)  # convert all to factors
punt <- as.data.frame(punt)

punt <- select(punt, -c(8)) # remove refs 

punt <- as.data.frame(t(punt)) # transpose

# kappa
w <- kappam.fleiss(punt[, 1:912]) # kappa = 0.33


# The Vaults INTERRATER RELIABILITY: ############################################
vault <- `name[The Vaults`

vault <- lapply(vault, factor)  # convert all to factors
vault <- as.data.frame(vault)

vault <- select(vault, -c(8)) # remove refs 

vault <- as.data.frame(t(vault)) # transpose

# kappa
x <- kappam.fleiss(vault[, 1:581]) # kappa = 0.37


# The Waterman INTERRATER RELIABILITY: ############################################
water <- `name[The Waterman`

water <- lapply(water, factor)  # convert all to factors
water <- as.data.frame(water)

water <- select(water, -c(8)) # remove refs 

water <- as.data.frame(t(water)) # transpose

# kappa
y <- kappam.fleiss(water[, 1:262]) # kappa = 0.58

# The Wrestlers INTERRATER RELIABILITY: ############################################
wrestle <- `name[The Wrestlers`

wrestle <- lapply(wrestle, factor)  # convert all to factors
wrestle <- as.data.frame(wrestle)

wrestle <- select(wrestle, -c(8)) # remove refs 

wrestle <- as.data.frame(t(wrestle)) # transpose

# kappa
z <- kappam.fleiss(wrestle[, 1:991]) # kappa = 0.35

# Travellers Rest Beefeater INTERRATER RELIABILITY: ############################################
trb <- `name[Travellers Rest Beefeater`

trb <- lapply(trb, factor)  # convert all to factors
trb <- as.data.frame(trb)

trb <- select(trb, -c(8)) # remove refs 

trb <- as.data.frame(t(trb)) # transpose

# kappa
aa <- kappam.fleiss(trb[, 1:96]) # kappa = 0.65


# Wildwood Rest Beefeater INTERRATER RELIABILITY: ############################################
wild <- `name[Wildwood`

wild <- lapply(wild , factor)  # convert all to factors
wild <- as.data.frame(wild)

wild <- select(wild, -c(8)) # remove refs 

wild <- as.data.frame(t(wild)) # transpose

# kappa
ab <- kappam.fleiss(wild[, 1:342]) # kappa = 0.41

# Zizzi INTERRATER RELIABILITY: ############################################
ziz <- `name[Zizzi`

ziz <- lapply(ziz, factor)  # convert all to factors
ziz <- as.data.frame(ziz)

ziz <- select(ziz, -c(8)) # remove refs 

ziz <- as.data.frame(t(ziz)) # transpose

# kappa
ac <- kappam.fleiss(ziz[, 1:32]) # kappa = 0.48


### Now put all the lists of kappas together
a <- a$value
b <- b$value
c <- c$value
d <- d$value
e <- e$value
f <- f$value
g <- g$value
h <- h$value
i <- i$value
j <- j$value
k <- k$value
l <- l$value
m <- m$value
n <- n$value
o <- o$value
p <- p$value
q <- q$value
r <- r$value
s <- s$value
t <- t$value
u <- u$value
v <- v$value
w <- w$value
x <- x$value
y <- y$value
z <- z$value
aa <- aa$value
ab <- ab$value
ac <- ac$value





id <- c("Loch Fyne", "Alimentum", "Aromi", "Bibimbap House", "Blue Spice", "Browns Cambridge",
        "Clowns", "Cocum", "Cotto", "Fitzabilities", "Giraffe", "Green Man", "Midsummer House",
        "Strada", "Taste of Cambridge", "The Cambridge Blue", "The Cricketers", "The Eagle",
        "The Golden Palace", "The Mill", "The Phoenix", "The Plough", "The Punter", "The Vaults",
        "The Waterman", "The Wrestlers", "Travellers Rest Beefeater", "Wildwood", "Zizzi")

kappa <- c(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u,v,w,x,y,z, aa, ab, ac)

data <- data.frame(id, kappa)
data

mean(data$kappa) # mean=0.51
sd(data$kappa) # mean=0.11

# 1 sd above the mean = 0.62 +
# Midsummer House, Travellers Rest Beefeater, The Plough, The Cambridge Blue, Taste of Cambridge 

# 1 sd below the mean = 0.40 - 
# The Punter, The Cricketers, The Wrestlers, The Mill, The Eagle, The Vaults, Blue Spice


data <- data[order(kappa),]
data
```


Data viz
```{r}
library(ggplot2)
library(RColorBrewer)

data <- as_tibble(data)
data$id <- as.factor(data$id)
data$kappa <- as.numeric(data$kappa)

# add column with SD placement

data$newkappa <- ifelse(data$kappa < 0.41, -1, 0)
data$newkappa <- ifelse(data$kappa > 0.62, 1, 0)
data
data$newkappa <- as.factor(data$newkappa)


g <- ggplot(data=data,
            aes(x=id, y=kappa) +
  geom_bar(sta='identity', aes(fill = data$newkappa)) +
  scale_fill_gradient2(low='pink', mid='cyan', high='green'))

g


data$id <- as.character(data$id) # character
class(data$kappa) # numeric
data$newkappa <- as.numeric(data$newkappa) # numeric

range(data$kappa)


library(devtools)
devtools::install_github("stefan-schroedl/plotluck")
library(plotluck)


plotluck(data, kappa~id)

```





























Split 70/30
```{r}

smp_size <- floor(0.7 * nrow(dev_test_combo))

set.seed(1234) # set the seed for reproducibility
train_ind <- sample(seq_len(nrow(dev_test_combo)), size = smp_size)

train70 <- dev_test_combo[train_ind, ] # 70% training df 
test30 <- dev_test_combo[-train_ind, ] # 30% testing df 

```

Check out the interrater reliability of restaurant reviews in dev_test_combo
```{r}
dev_test_combo

# First split into more columns on comma
df <- data.frame(do.call('rbind', strsplit(as.character(dev_test_combo$mr),',',fixed=TRUE)))


df <- data.frame(x = c("x", "x y", "x y z", NA))
df %>% separate(x, c("a", "b"))

library()
df <- dev_test_combo %>% separate(mr, 
                c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12"))




df <- data.frame(do.call('rbind', strsplit(as.character(dev_test_combo),',',fixed=TRUE)))
df

```

















Clean it up
```{r}
# text = dev_refs
dev_refs <- devset$ref # pull out the text column

# normalize:
dev_refs <- tolower(dev_refs)
dev_refs <- removePunctuation(dev_refs)

devset["cleanrefs"] <- dev_refs # add clean text column back to df
head(devset$cleanrefs, 10)


# add <START> and <END> tokens
devset$cleanrefs <- 
  paste("<START>", devset$cleanrefs,
        sep="_")

devset[-length(devset)] <- paste0(devset[-length(devset)], '<END>')
strsplit(paste(devset, collapse='<END> '), ' ')[[1]]     


```


# Input = delexicalized MRs (different from tgen)

Create corpus
```{r}
# devset refs corpus:
dev_corpus_refs <- Corpus(VectorSource(devset$ref))
dev_corpus_refs

```


Normalization: lowercase the words, remove punctuation and numbers, remove whitespace
```{r}
# devset refs normalize:
dev_corpus_refs <- tolower(dev_corpus_refs)
dev_corpus_refs <- removeNumbers(dev_corpus_refs)
dev_corpus_refs <- removePunctuation(dev_corpus_refs)
dev_corpus_refs <- stripWhitespace(dev_corpus_refs)

# remove backslashes:
## convert corpus to string
toString(dev_corpus_refs)


```


Add <start> and <end> tokens to beginning, end of each sentence 
```{r}



```


Replace all values in MRs with corresponding semantic name of the slot (delexicalization)




https://datamathstat.wordpress.com/2019/10/25/text-preprocessing-for-nlp-and-machine-learning-using-r/
```{r}
text_corpus <- (VectorSource(devset))
   text_corpus <- Corpus(text_corpus)
   summary(text_corpus)
   
##Tokenization: Split a text into single word terms called "unigrams" 
text_corpus_clean<-Boost_tokenizer(text_corpus)
 # text_corpus_clean[[5]]$content

#Normalization: lowercase the words and remove punctuation and numbers
text_corpus_clean<-tm_map(text_corpus , content_transformer(tolower))
text_corpus_clean <- tm_map(text_corpus_clean, removePunctuation)
text_corpus_clean <- tm_map(text_corpus_clean, removeNumbers)
text_corpus_clean <- tm_map(text_corpus_clean, stripWhitespace)

##Remove stopwords and custom stopwords
text_corpus_clean <- c(stopwords('english'), "a", "b") 



```





Turn data into a corpus for text processing
```{r}

#devset corpus:
devset_corpus <- corpus(devset, text_field = "ref")
print(devset_corpus)
summary(devset_corpus, 10)


```

Tokenization of devset
```{r}
devset_corpus_tok <- tokenize_words(devset_corpus)
devset_corpus_clean <- devset_corpus_tok

devset_corpus_clean
```

Normalize devset
  + all lower case
  + remove punctuation, numbers, white spaces
  + remove stop words, sparce terms
```{r}
# devset_corpus_clean <- tolower(devset_corpus_clean)
devset_corpus_clean <- removePunctuation(devset_corpus_clean)
devset_corpus_clean <- removeNumbers(devset_corpus_clean)
devset_corpus_clean <- stripWhitespace(devset_corpus_clean)
devset_corpus_clean <- removeWords(devset_corpus_clean, stopwords('en'))
```


Visualize the pre-processed data
```{r}
dtm <- DocumentTermMatrix(devset_corpus_clean)


```
















